Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization

### 2020-02-07 WRITEUP/ms_referee.tex
final edits

\citestyle{aa}
\shorttitle{Dynamical Properties of MCCs in Galaxies at the EoR}
\shortauthors{Leung et al.}

\begin{document}
\title{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization}

@@

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the epoch of reionization using cosmological zoom-in simulations. We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
and the Next Generation Very Large Array.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
%
Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs) that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}). Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
Even in the local Universe, where detailed \obs can be made, variations in molecular cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
{\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
and morphologies of galaxies out to the EoR and their importance on providing
the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}.
Compared to the zoom-in galaxies presented in these work,
the simulation used here focuses on an LBG galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
(see \citealt{Pallottini19a} for a detailed comparison between these cosmological zoom-in simulations).
}

%
While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
%
On the theoretical side, a schematic investigation by \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist of many smaller clumps formed by gravitational instability, a hierarchical structure that persists in an idealized disk model by \citet{Behrendt19}.

To understand the physical properties of MCCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MCCs in prototypical (i.e., $L^*$) galaxies in the epoch of reionization (EoR).

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify MCCs, and present the formalism within which we interpret the results. In \Sec{results}, we present the results and characteristic properties of the MCCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%

\section{Physical Background}\label{sec:Back}
We begin by introducing some empirical relations commonly mentioned in observational studies of molecular clouds in the literature, as well as describing the gravitational instability of galactic disks, which might be driving MCC formation. These concepts will be used in the subsequent analysis of our simulations.

@@

The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the
Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and
$\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass {\bf enclosed} within the MCC volume.

@@

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$,
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
{\bf In the simulation, the UV radiation field is assumed to be uniform spatially.
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as
part of the \ncode{Krome} network. % (see \citealt{Bovino16a}).
We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
%
Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
%
These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}). We are interested in determining whether MCC properties are sensitive to these different dynamical conditions. For completeness, we also show relationships of MCC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).

\section{Molecular Cloud Complexes}\label{sec:eqn}

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%!TEX encoding = UTF-8 Unicode
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles.
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
\label{fig:MCC}
}
\end{figure*}

In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
%
In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs are selected at $n_{\rm cut} \leq n_{\rm H2}$. We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$. Note that with these choices we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).

To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}). Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections so that the identification can be more easily appreciated.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

\subsection{MCC Properties} \label{sec:distribution}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating the global quantities of MCCs, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC.
We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
%The bulk velocity dispersion is
%\begin{equation}
%\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
%\end{equation}
{\bf The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,,
\end{equation}
where \Eq{defineaverage} is applied to each velocity component.
}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

\subsection{Synthetic vs Observed MCC Properties} \label{sec:diss1}

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.

>>>>

\citestyle{aa}
\shorttitle{Dynamical Properties of MGCs in Galaxies at the EoR}
\shortauthors{Leung et al.}

\begin{document}
\title{Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization}

@@

\begin{abstract}
We study the properties of molecular-forming gas clumps (MGCs) at the epoch of reionization using cosmological zoom-in simulations. We identify MGCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MGC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MGCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MGCs. We find that MGCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in {\bf clouds} and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
and the Next Generation Very Large Array.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
%
Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of 
{\bf dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{{\bf Note that by clumps, 
we refer to kiloparsec-scale gas concentrations in galaxies, rather than molecular gas concentrations small than molecular clouds 
and containing cores.}}; 
MGCs)} that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}). Some theoretical works argue that the migration of such giant massive clumps through disks is largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
Even in the local Universe, where detailed \obs can be made, variations in molecular cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of 
MGCs in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
{\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
and morphologies of galaxies out to the epoch of reionization (EoR) and their importance for providing
the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}.
Compared to the zoom-in galaxies presented in these works,
the simulation used here focuses on a Lyman-break galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
(see \citealt{Pallottini19a} for a comparison between these zoom-in simulations).
Most notably, we include a non-equilibrium thermo-chemical network to follow the formation of H$_2$, which is 
crucial to examining the properties of MGCs.
}

%
While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
%
On the theoretical side, a schematic investigation by \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist of many smaller clouds formed by gravitational instability, a hierarchical structure that persists in an idealized disk model by \citet{Behrendt19}.

To understand the physical properties of MGCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MGCs in prototypical (i.e., $L^*$) galaxies in the EoR.

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify MGCs, and present the formalism within which we interpret the results. In \Sec{results}, we present the results and characteristic properties of the MGCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%

\section{Physical Background}\label{sec:Back}
We begin by introducing some empirical relations commonly mentioned in observational studies of molecular clouds in the literature, as well as describing the gravitational instability of galactic disks, which might be driving MGC formation. These concepts will be used in the subsequent analysis of our simulations.

@@

The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the
Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
the gas {\bf (including thermal, turbulent, and bulk motions)}, $\mathcal{T}_{\rm ext}$ is external pressure support, and
$\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass {\bf enclosed} within the MGC volume.

@@

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$,
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
{\bf In the simulation, the UV radiation field is assumed to be uniform spatially.
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
while the formation rate on dust grain is computed following \citet{Jura75a}. Photo-dissociation via Lyman-Werner photons is included as
part of the \ncode{Krome} network. % (see \citealt{Bovino16a}).
We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun (see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MGC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
%
Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
%
These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}). We are interested in determining whether MGC properties are sensitive to these different dynamical conditions. For completeness, we also show relationships of MGC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).

\section{Molecular-forming Gas Clumps}\label{sec:eqn}

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MGCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%!TEX encoding = UTF-8 Unicode
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles.
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
\label{fig:MGC}
}
\end{figure*}

In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
%
In each evolutionary stage, we identify MGCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MGCs are selected at $n_{\rm cut} \leq n_{\rm H2}$. We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$. Note that with these choices we are including MGCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).

To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MGC}). Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections so that the identification can be more easily appreciated.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

\subsection{MGC Properties} \label{sec:distribution}

@@

The mass of an MGC is calculated from the uniformly-gridded 3D density field, integrating over the MGC volume $V$. The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MGCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MGCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating the global quantities of MGCs, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MGC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MGC.
We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
%The bulk velocity dispersion is
%\begin{equation}
%\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
%\end{equation}
{\bf The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,,
\end{equation}
where \Eq{defineaverage} is applied to each velocity component.
}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

\subsection{Synthetic vs Observed MGC Properties} \label{sec:diss1}

In this section, we compare the observable quantities of MGCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
